---
title: "na_fixing_albert"
author: "Albert"
date: '2022-06-10'
output: html_document
---

# Library
```{r setup, include = TRUE, warning = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(here)
library(fs)

```

# A description of the issue
Due to unknown errors, Pavlovia records keyboard responses in two fashions:
The first one is that participants' response (either f or j) to a particular trial is recorded in a separate row from their replay input, which is recorded as "r" in another line. 
The second one is their f/j response is recorded in the same row, side by side with the replay response. 
This causes our cleaning function wipe out their f and j response, resulting in 19 NA values. 
This script is intended to pick out the irregularly, storing csv files and fixing them.

# Check NA in training/phono_test/alt_test choices
## Check choices that contain na values
```{r}
study_full_final <- read.csv(here("data", "cleaned", "full_process_albert.csv"))
nas <- study_full_final %>% 
  filter(is.na(choice)) 
nas
```

## Find Participants that made these choices
```{r}
na_participants <- unique(nas$participant)
na_participants
```

## Construct File Names that Pavlovia Recorded
```{r}
na_participants <- study_full_final %>% 
  filter(is.na(choice)) %>% 
  select(participant, study_name, date) %>% 
  group_by(participant, study_name) %>% 
  unique() %>% 
  mutate(file_prefix = str_remove_all(participant, ":"),
         file_infix = study_name, 
         file_suffix = date) %>% 
  mutate(file_name = paste0(file_prefix, "_", file_infix, "_", file_suffix)) %>% 
  mutate(file_name = paste0(file_name, ".csv")) %>% 
  mutate(file_name = str_remove_all(file_name, "[+]")) %>% 
  ungroup() %>% 
  select(file_name, study_name)
```

## Move these files to a separate folder for later automatic processing and visual inspection
### Define a function for moving irregular files
```{r}
library(fs)
find_na_participants <- function(study){
  study_folder = str_remove(study, "_")
  files <- na_participants %>% 
    filter(study_name == study)
  
  files_list <- unlist(files)
  
  oldDir <- here("data", 
                 "data_finished", 
                 paste0(study_folder, "/"))
  dir.create(here("data", 
                  "na_participants", 
                  paste0(study_folder, "/")))
  newDir = here("data", 
                "na_participants", 
                paste0(study_folder, "/"))
  
  for (i in 1:length(files_list)){
  file.copy(
    from = paste0(oldDir, files_list[i]), 
    to = paste0(newDir, files_list[i]), 
    overwrite = TRUE, 
    recursive = FALSE, 
    copy.mode = FALSE, 
    copy.date = FALSE)
}
}
```

### Excute the function with all studies
```{r}
find_na_participants(study = "study_1")
find_na_participants(study = "study_2")
find_na_participants(study = "study_3")
find_na_participants(study = "study_4")
```

# Set up a function to fix the issue described
```{r}
library(tidyverse)

fix_na <- function(study){
  files <- 
    na_participants %>% 
    filter(study_name == study) %>% 
    select(-study_name)
  
  files_list <-    unlist(files)
  study_folder <-  str_remove_all(study, "_")
  
  dir.create(here("data", 
                  "data_fixed", 
                  "na_fixed", 
                   study_folder))
  
    for (i in 1:length(files_list)){
      
      raw_data <-  read.csv(here("data", 
                                 "na_participants", 
                                  study_folder, 
                                  files_list[i]))
      fixed <- 
        raw_data %>% 
        mutate(sliced = case_when(
          key_resp_22.keys == "space" & key_resp_21.keys == ""~"yes",
          key_resp_3.keys == "space" & key_resp_15.keys == ""~"yes",
          key_resp_20.keys == "r" & key_resp_21.keys == ""~"yes",
          key_resp_23.keys == "r" & key_resp_15.keys == ""~"yes"
        )) %>% 
        filter(is.na(sliced)|!sliced == "yes")
      
       write_csv(fixed, 
                 here("data", 
                      "data_fixed", 
                      "na_fixed", 
                       study_folder, 
                       files_list[i]))
  }
}
```

## Apply the function with all the studies
```{r}
fix_na(study = 'study_1')
fix_na(study = 'study_2')
fix_na(study = 'study_3')
fix_na(study = 'study_4')
```

## Set up a function to move back all fixed files
```{r}
put_back_na <- function(study){
  study_folder = str_remove(study, "_")
  files <- na_participants %>% 
    filter(study_name == study)
  files_list <- unlist(files)
  newDir <- here("data", 
                 "data_fixed", 
                 paste0(study_folder, "/"))
  oldDir = here("data", 
                "data_fixed", 
                "na_fixed", 
                paste0(study_folder, "/"))
  for (i in 1:length(files_list)){
  file.copy(
    from = paste0(oldDir, files_list[i]), 
    to = paste0(newDir, files_list[i]), 
    overwrite = TRUE, 
    recursive = FALSE, 
    copy.mode = FALSE, 
    copy.date = FALSE)
}
}
```

## Move things back
```{r}
put_back_na("study_1")
put_back_na("study_2")
put_back_na("study_3")
put_back_na("study_4")
```