---
title: "cleaning_ABD"
author: "Albert, Xiaoyu"
date: '2022-06-06'
output: html_document
---

# Library
```{r setup, include = TRUE, warning = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  comment = "#>"
)
library(knitr)
library(tidyverse)
library(here)
library(broom)
library(broom.mixed)
library(writexl)
library(ggpubr)
library(gghighlight)
library(lme4)
library(lmerTest)
library(fs)

```

## Note from Albert for your reference :)
This version cancels the process within each function that identifies which pattern participants chose. Instead, it only processes which key participants have pressed. It later imports the condition files we use in the experiment to identify regular/random pattern. Also, by changing all f (or FALSE, as coerced by R) and j to f_key and j_key, there will be no (or very few) NA value in the choice column.

# Data
```{r}
list_study1 <- dir_ls(here("data", "data_fixed", "study1"), regexp = ".csv$")
list_study2 <- dir_ls(here("data", "data_fixed", "study2"), regexp = ".csv$")
list_study3 <- dir_ls(here("data", "data_fixed", "study3"), regexp = ".csv$")
list_study4 <- dir_ls(here("data", "data_fixed","study4"), regexp = ".csv$")
```

# Cleaning Function for Study 1 and 2
```{r}
cleanup12 <- function(csvfile){
  
  # read in raw data from the data list
  raw_data <- read_csv(csvfile) %>% 
    select(-key_resp_23.keys)
  
  
  # clean the training phase data
  training <- 
    raw_data %>% 
    select(posgreen,
           posyellow,
           participant,
           date,
           expName,
           exp_item_num = item_num,
           phase = item_type,
           exp_green_sg = green_stem,
           exp_green_pl = green_full,
           exp_yellow_sg = yellow_stem,
           exp_yellow_pl = yellow_full,
           exp_choice_key = planet_selector_key_training.keys,
           exp_rt = planet_selector_key_training.rt,
           exp_trial_order = trials_7.thisN,
           round = training_num) %>% 
    fill(c("posgreen", "posyellow"), .direction = "down") %>% 
    mutate(across(posgreen:posyellow,
                  ~ str_extract(.x, "(?<=\\[).+(?=\\,)"))) %>% 
    mutate(f_choice = case_when(
      posgreen < 0 ~ "green",
      posgreen > 0 ~ "yellow"
    ),
    j_choice = case_when(
      posgreen < 0 ~ "yellow",
      posgreen > 0 ~ "green"
    )) %>% 
    relocate(f_choice, .before = "participant") %>% 
    relocate(j_choice, .after = "f_choice") %>% 
    fill(round, .direction = "up") %>% 
    mutate(exp_choice_key = lag(exp_choice_key),
           exp_rt = lag(exp_rt),
           exp_trial_order = exp_trial_order + 1) %>%
    filter(phase == "training") %>% 
    mutate(exp_choice_planet = case_when(
      exp_choice_key == "f" ~ f_choice,
      exp_choice_key == "j" ~ j_choice
    )) %>% 
    relocate(phase, round, exp_trial_order, .before = exp_item_num) %>% 
    relocate(exp_choice_planet, .before = exp_rt)

  # Fixed_1
  training$exp_choice_key <- as.character(training$exp_choice_key)
  
  
  # clean the phonotactics test phase data
  phono_test <-
    raw_data %>% 
    select(
      posgreen,
      posyellow,
      expName,
      participant,
      date,
      phono_test_item_num = item_num,
      phono_test_choice_key = key_resp_21.keys,
      phase = stage,
      phono_choice_A = choice_A,
      phono_choice_A_property = choice_A_property,
      phono_choice_B = choice_B,
      phono_choice_B_property = choice_B_property,
      phono_choice_rt = key_resp_21.rt,
      # phono_next_rt = key_resp_21.rt,
      item_type
    ) %>% 
    fill(c("posgreen", "posyellow"), .direction = "down") %>% 
    mutate(across(posgreen:posyellow,
                  ~ str_extract(.x, "(?<=\\[).+(?=\\,)"))) %>% 
    mutate(f_choice = case_when(
      posgreen < 0 ~ "choice_A",
      posgreen > 0 ~ "choice_B"
    ),
    j_choice = case_when(
      posgreen < 0 ~ "choice_B",
      posgreen > 0 ~ "choice_A"
    )) %>% 
    relocate(f_choice, .before = "participant") %>% 
    relocate(j_choice, .after = "f_choice") %>%
    fill(item_type, .direction = "up") %>% 
    filter(is.na(item_type)) %>% 
    mutate(phono_test_choice_key = lag(phono_test_choice_key),
           phono_choice_rt = lag(phono_choice_rt)
           ) %>% 
    fill(phase, .direction = "up") %>% 
    filter(phase == "phono_test") %>% 
    select(posgreen:phono_choice_rt) %>% 
    filter(!is.na(phono_test_item_num)) %>% 
    mutate(phono_test_trial_order = c(1:8),
           phono_old_new = case_when(
             str_detect(phono_choice_A, "s|f") ~ "new",
             TRUE ~ "old"
           ),
           phono_choice = case_when(
             phono_test_choice_key == "f" ~ f_choice,
             phono_test_choice_key == "j" ~ j_choice
           )) %>% 
    mutate(phono_choice = case_when(
      phono_choice == "choice_A" ~ phono_choice_A,
      phono_choice == "choice_B" ~ phono_choice_B
    )) %>% 
    relocate(expName, 
             phase, 
             phono_test_trial_order,
             phono_test_item_num,
             phono_old_new,
             phono_choice_A,
             phono_choice_B,
             phono_test_choice_key,
             phono_choice,
             phono_choice_rt,
             # phono_next_rt,
             .after = date)
  # Fixed 2
  phono_test$phono_test_choice_key <- as.character(phono_test$phono_test_choice_key)
  
  
  
  # clean the alternation test phase data
  alt_test <-
    raw_data %>% 
    select(
      posgreen,
      posyellow,
      participant,
      date,
      expName,
      phase = stage,
      alt_test_item_num = item_num,
      alt_choice_A = choice_A,
      alt_choice_A_property = choice_A_property,
      alt_choice_B = choice_B,
      alt_choice_B_property = choice_B_property,
      alt_test_choice_key = key_resp_15.keys,
      alt_choice_rt = key_resp_15.rt,
      # alt_next_rt = key_resp_3.rt,
      item_type
    ) %>%
    fill(c("posgreen", "posyellow"), .direction = "down") %>% 
    mutate(across(posgreen:posyellow,
                  ~ str_extract(.x, "(?<=\\[).+(?=\\,)"))) %>% 
    mutate(f_choice = case_when(
      posgreen < 0 ~ "choice_A",
      posgreen > 0 ~ "choice_B"
    ),
    j_choice = case_when(
      posgreen < 0 ~ "choice_B",
      posgreen > 0 ~ "choice_A"
    )) %>% 
    relocate(f_choice, .before = "participant") %>% 
    relocate(j_choice, .after = "f_choice") %>%
    fill(item_type, .direction = "up") %>% 
    filter(is.na(item_type)) %>% 
    mutate(alt_test_choice_key = lag(alt_test_choice_key),
           alt_choice_rt = lag(alt_choice_rt)
           ) %>%
    fill(phase, .direction = "up") %>% 
    filter(phase == "alt_test") %>% 
    select(posgreen:alt_choice_rt) %>% 
    filter(!is.na(alt_test_item_num)) %>% 
    mutate(alt_test_trial_order = c(1:12),
           alt_old_new = case_when(
             str_detect(alt_choice_A, "s|f") ~ "new",
             TRUE ~ "old"
           ),
           alt_choice = case_when(
             alt_test_choice_key == "f" ~ f_choice,
             alt_test_choice_key == "j" ~ j_choice
           )) %>% 
    mutate(alt_choice = case_when(
      alt_choice == "choice_A" ~ alt_choice_A,
      alt_choice == "choice_B" ~ alt_choice_B
    )) %>% 
    relocate(alt_test_trial_order, .before = alt_test_item_num) %>% 
    relocate(alt_old_new, .after = alt_test_item_num) %>% 
    relocate(alt_choice, .after = alt_test_choice_key)
  # Fixed 3
  alt_test$alt_test_choice_key <- as.character(alt_test$alt_test_choice_key)
  phono_test$phono_test_choice_key <- as.character(phono_test$phono_test_choice_key)
  training$exp_choice_key <- as.character(training$exp_choice_key)
  
  # combine the three phases
  full_ <-
    full_join(training, phono_test, by = c("posgreen",
                                           "posyellow",
                                           "f_choice",
                                           "j_choice",
                                           "participant", 
                                           "date",
                                           "expName",
                                           "phase")) %>% 
    full_join(alt_test, by = c("posgreen",
                               "posyellow",
                               "f_choice",
                               "j_choice",
                               "participant", 
                               "date",
                               "expName",
                               "phase")) %>% 
    mutate(
      exp_choice_key = case_when(
        exp_choice_key == "f" | exp_choice_key == "FALSE"~"f_key",
        exp_choice_key == "j"~"j_key"
      )) %>% 
    mutate(
      alt_test_choice_key = case_when(
        alt_test_choice_key == "f" | alt_test_choice_key == "FALSE"~"f_key",
        alt_test_choice_key == "j"~"j_key"
      )
    ) %>% 
    mutate(
      phono_test_choice_key = case_when(
        phono_test_choice_key == "f" | phono_test_choice_key == "FALSE"~"f_key",
        phono_test_choice_key == "j" ~ "j_key"
      )
    )
  
}
```

# Clearing Function for Study 3 and 4
```{r}
cleanup34 <- function(csvfile){
  
  # read in raw data from the data list
  raw_data <- read_csv(csvfile) %>% 
    select(-key_resp_23.keys)
  
  
  # clean the training phase data
  training <- 
    raw_data %>% 
    select(posgreen,
           posyellow,
           participant,
           date,
           expName,
           imp_item_num = item_num,
           phase = item_type,
           imp_green_choice = green_all,
           imp_green_stem = green_stem,
           imp_green_property = green_property,
           imp_yellow_choice = yellow_all,
           imp_yellow_stem = yellow_stem,
           imp_yellow_property = yellow_property,
           imp_stimuli_type = stimuli_type,
           imp_choice_key = planet_selector_key_training.keys,
           imp_rt = planet_selector_key_training.rt,
           imp_trial_order = trials_7.thisN,
           round = training_num) %>% 
    fill(c("posgreen", "posyellow"), .direction = "down") %>% 
    mutate(across(posgreen:posyellow,
                  ~ str_extract(.x, "(?<=\\[).+(?=\\,)"))) %>% 
    mutate(f_choice = case_when(
      posgreen < 0 ~ "green",
      posgreen > 0 ~ "yellow"
    ),
    j_choice = case_when(
      posgreen < 0 ~ "yellow",
      posgreen > 0 ~ "green"
    )) %>% 
    relocate(f_choice, .before = "participant") %>% 
    relocate(j_choice, .after = "f_choice") %>% 
    fill(round, .direction = "up") %>% 
    mutate(imp_choice_key = lag(imp_choice_key),
           imp_rt = lag(imp_rt),
           imp_trial_order = imp_trial_order + 1) %>%
    filter(phase == "training") %>% 
    mutate(imp_choice_planet = case_when(
      imp_choice_key == "f" ~ f_choice,
      imp_choice_key == "j" ~ j_choice
    )) %>% 
    relocate(phase, round, imp_trial_order, .before = imp_item_num) %>% 
    relocate(imp_choice_planet, .before = imp_rt)
  
  training$imp_choice_key <- as.character(training$imp_choice_key)
  
  # clean the phonotactics test phase data
  phono_test <-
    raw_data %>% 
    select(
      posgreen,
      posyellow,
      expName,
      participant,
      date,
      phono_test_item_num = item_num,
      phono_test_choice_key = key_resp_21.keys,
      phase = stage,
      phono_choice_A = choice_A,
      phono_choice_A_property = choice_A_property,
      phono_choice_B = choice_B,
      phono_choice_B_property = choice_B_property,
      phono_choice_rt = key_resp_21.rt,
      # phono_next_rt = key_resp_21.rt,
      item_type
    ) %>% 
    fill(c("posgreen", "posyellow"), .direction = "down") %>% 
    mutate(across(posgreen:posyellow,
                  ~ str_extract(.x, "(?<=\\[).+(?=\\,)"))) %>% 
    mutate(f_choice = case_when(
      posgreen < 0 ~ "choice_A",
      posgreen > 0 ~ "choice_B"
    ),
    j_choice = case_when(
      posgreen < 0 ~ "choice_B",
      posgreen > 0 ~ "choice_A"
    )) %>% 
    relocate(f_choice, .before = "participant") %>% 
    relocate(j_choice, .after = "f_choice") %>%
    fill(item_type, .direction = "up") %>% 
    filter(is.na(item_type)) %>% 
    mutate(phono_test_choice_key = lag(phono_test_choice_key),
           phono_choice_rt = lag(phono_choice_rt)
           ) %>% 
    fill(phase, .direction = "up") %>% 
    filter(phase == "phono_test") %>% 
    select(posgreen:phono_choice_rt) %>% 
    filter(!is.na(phono_test_item_num)) %>% 
    mutate(phono_test_trial_order = c(1:8),
           phono_old_new = case_when(
             str_detect(phono_choice_A, "s|f") ~ "new",
             TRUE ~ "old"
           ),
           phono_choice = case_when(
             phono_test_choice_key == "f" ~ f_choice,
             phono_test_choice_key == "j" ~ j_choice
           )) %>% 
    mutate(phono_choice = case_when(
      phono_choice == "choice_A" ~ phono_choice_A,
      phono_choice == "choice_B" ~ phono_choice_B
    )) %>% 
    relocate(expName, 
             phase, 
             phono_test_trial_order,
             phono_test_item_num,
             phono_old_new,
             phono_choice_A,
             phono_choice_A_property,
             phono_choice_B,
             phono_choice_B_property,
             phono_test_choice_key,
             phono_choice,
             phono_choice_rt,
             # phono_next_rt,
             .after = date)
  
  phono_test$phono_test_choice_key <- as.character(phono_test$phono_test_choice_key)
  
  # clean the alternation test phase data
  alt_test <-
    raw_data %>% 
    select(
      posgreen,
      posyellow,
      participant,
      date,
      expName,
      phase = stage,
      alt_test_item_num = item_num,
      alt_choice_A = choice_A,
      alt_choice_A_property = choice_A_property,
      alt_choice_B = choice_B,
      alt_choice_B_property = choice_B_property,
      alt_test_choice_key = key_resp_15.keys,
      alt_choice_rt = key_resp_15.rt,
      # alt_next_rt = key_resp_3.rt,
      item_type
    ) %>%
    fill(c("posgreen", "posyellow"), .direction = "down") %>% 
    mutate(across(posgreen:posyellow,
                  ~ str_extract(.x, "(?<=\\[).+(?=\\,)"))) %>% 
    mutate(f_choice = case_when(
      posgreen < 0 ~ "choice_A",
      posgreen > 0 ~ "choice_B"
    ),
    j_choice = case_when(
      posgreen < 0 ~ "choice_B",
      posgreen > 0 ~ "choice_A"
    )) %>% 
    relocate(f_choice, .before = "participant") %>% 
    relocate(j_choice, .after = "f_choice") %>%
    fill(item_type, .direction = "up") %>% 
    filter(is.na(item_type)) %>% 
    mutate(alt_test_choice_key = lag(alt_test_choice_key),
           alt_choice_rt = lag(alt_choice_rt)
           ) %>%
    fill(phase, .direction = "up") %>% 
    filter(phase == "alt_test") %>% 
    select(posgreen:alt_choice_rt) %>% 
    filter(!is.na(alt_test_item_num)) %>% 
    mutate(alt_test_trial_order = c(1:12),
           alt_old_new = case_when(
             str_detect(alt_choice_A, "s|f") ~ "new",
             TRUE ~ "old"
           ),
           alt_choice = case_when(
             alt_test_choice_key == "f" ~ f_choice,
             alt_test_choice_key == "j" ~ j_choice
           )) %>% 
    mutate(alt_choice = case_when(
      alt_choice == "choice_A" ~ alt_choice_A,
      alt_choice == "choice_B" ~ alt_choice_B
    ),
    alt_choice_property = case_when(
      alt_choice == alt_choice_A ~ alt_choice_A_property,
      alt_choice == alt_choice_B ~ alt_choice_B_property
    )) %>% 
    relocate(alt_test_trial_order, .before = alt_test_item_num) %>% 
    relocate(alt_old_new, .after = alt_test_item_num) %>% 
    relocate(alt_choice, .after = alt_test_choice_key)
  
  alt_test$alt_test_choice_key <- as.character(alt_test$alt_test_choice_key)
  
  # fixing character/logical issue
  training$imp_choice_key <- as.character(training$imp_choice_key)
  phono_test$phono_test_choice_key <- as.character(phono_test$phono_test_choice_key)
  alt_test$alt_test_choice_key <- as.character(alt_test$alt_test_choice_key)
  
  # combine the three phases
  full_ <-
    full_join(training, phono_test, by = c("posgreen",
                                           "posyellow",
                                           "f_choice",
                                           "j_choice",
                                           "participant", 
                                           "date",
                                           "expName",
                                           "phase")) %>% 
    full_join(alt_test, by = c("posgreen",
                               "posyellow",
                               "f_choice",
                               "j_choice",
                               "participant", 
                               "date",
                               "expName",
                               "phase")) %>% 
    mutate(
      imp_choice_key = case_when(
        imp_choice_key == "f" | imp_choice_key == "FALSE"~"f_key",
        imp_choice_key == "j"~"j_key"
      )) %>% 
    mutate(
      alt_test_choice_key = case_when(
        alt_test_choice_key == "f" | alt_test_choice_key == "FALSE"~"f_key",
        alt_test_choice_key == "j"~"j_key"
      )
    ) %>% 
    mutate(
      phono_test_choice_key = case_when(
        phono_test_choice_key == "f" | phono_test_choice_key == "FALSE"~"f_key",
        phono_test_choice_key == "j" ~ "j_key"
      )
    )
}
```

# Running the functions for each of the studies
```{r}
study1_full <- purrr::map_dfr(list_study1, cleanup12)
study2_full <- purrr::map_dfr(list_study2, cleanup12)
study3_full <- purrr::map_dfr(list_study3, cleanup34)
study4_full <- purrr::map_dfr(list_study4, cleanup34)
```

# Post-cleaning Processing
```{r}
# Merge dfs together
full_cleanup <- 
  full_join(study1_full, study2_full) %>% 
  full_join(study3_full) %>% 
  full_join(study4_full) 
```

# Rename expName with study_name
```{r}
full_cleanup <- rename(full_cleanup, c("study_name" = "expName"))
```

# Relocate implicit exp after explicit exp
```{r}
full_cleanup <-
  full_cleanup %>% 
  relocate(imp_trial_order:imp_rt, .after = exp_rt) 
```

# Add a column of study mode
```{r}
full_cleanup <- full_cleanup %>% 
  mutate(mode = case_when(
    study_name == "study_1" ~ "explicit",
    study_name == "study_2" ~ "explicit",
    study_name == "study_3" ~ "implicit",
    study_name == "study_4" ~ "implicit"
  )) %>% 
  relocate(mode, .before = study_name)
```

# Save the final version of the cleanup file
```{r}
write.csv(full_cleanup, here("data", "cleaned", paste0("full_cleanup_albert_", Sys.Date(), ".csv")))
```

# Add indication of exact trial of a single training session
## For tracing the decisions made by each of the participants in the training phase
```{r}
full_cleanup_training <- full_cleanup %>% 
  filter(phase == "training") %>% 
  group_by(participant) %>% 
  mutate(overall_trial_order = row_number()) %>% 
  relocate(overall_trial_order, .before = exp_green_sg)
```

# Further clean up
```{r}
data <- full_cleanup_training
```

## Training Part
### Select useful columns for each of the studies
```{r}
# For study 1 and 2
study12_training <- data %>% 
  filter(study_name %in% c("study_1", "study_2"), phase == "training") %>% 
  select(posgreen, posyellow, f_choice, j_choice, study_name, mode, participant, date, phase, round, exp_trial_order, 
         exp_item_num, overall_trial_order , exp_rt, exp_choice_planet,
         exp_choice_key) %>% 
  rename(
    trial_order = exp_trial_order,
    rt = exp_rt,
    choice_planet = exp_choice_planet,
    trial_order = exp_trial_order,
    item_num = exp_item_num,
    choice_key = exp_choice_key
  ) %>% 
  mutate(choice = case_when(
      choice_key == "f_key"&f_choice == "green" ~ "regular",
      choice_key == "j_key"&j_choice == "green" ~ "regular",
      choice_key == "f_key"&f_choice == "yellow" ~ "random",
      choice_key == "j_key"&j_choice == "yellow" ~ "random"
    )
  )

# For study 3 and 4
study34_training <- data %>% 
  filter(study_name %in% c("study_3", "study_4"), phase == "training") %>% 
  select(posgreen, posyellow, f_choice, j_choice, study_name, mode, participant, date, phase, round, imp_trial_order, 
         imp_item_num, overall_trial_order, imp_rt, imp_choice_planet,
         imp_choice_key) %>% 
  rename(
    trial_order = imp_trial_order,
    rt = imp_rt,
    choice_planet = imp_choice_planet,
    trial_order = imp_trial_order,
    item_num = imp_item_num,
    choice_key = imp_choice_key
  ) %>% 
  mutate(choice = case_when(
    choice_key == "f_key"&f_choice == "green" ~ "regular",
    choice_key == "j_key"&j_choice == "green" ~ "regular",
    choice_key == "f_key"&f_choice == "yellow" ~ "random",
    choice_key == "j_key"&j_choice == "yellow" ~ "random"
  )
  ) 

training_1 <- read.csv(here("data", "condition_files", "training_study_1.csv")) %>% 
  mutate(study_name = "study_1")
training_2<- read.csv(here("data", "condition_files", "training_study_2.csv")) %>% 
  mutate(study_name = "study_2")
training_12 <- rbind(training_1, training_2) %>% 
  separate(green_full, into = c("green_stem", "green_suffix")) %>% 
  separate(yellow_full, into = c("yellow_stem", "yellow_suffix")) %>% 
  relocate(study_name, .before = green_stem) %>% 
  mutate(item_sgpl = "sgpl")
training_3<- read.csv(here("data", "condition_files", "training_study_3.csv")) %>% 
  mutate(study_name = "study_3")
training_4<- read.csv(here("data", "condition_files", "training_study_4.csv")) %>% 
  mutate(study_name = "study_4")
training_34 <- rbind(training_3, training_4) %>% 
  separate(green_all, into = c("green_stem", "green_suffix"), sep = "-.*?") %>% 
  separate(yellow_all, into = c("yellow_stem", "yellow_suffix"), sep = "-.*?") %>% 
  relocate(study_name, .before = green_stem) %>% 
  select(item_num, item_type, study_name, green_stem, green_suffix, yellow_stem, yellow_suffix,
         stimuli_type) %>% 
  mutate(item_sgpl = stimuli_type) %>% 
  select(-stimuli_type)

training_condition <- rbind(training_12, training_34) %>% 
  rename('regular_stem' = "green_stem",
         'regular_suffix' = "green_suffix",
         'random_stem' = 'yellow_stem',
         'random_suffix' = 'yellow_suffix')
```

## Join two dfs of the training part
```{r}
study_training <- rbind(study12_training, study34_training) %>% 
  mutate(item_type = "training") %>% 
  select(-choice_planet)

study_training <- study_training %>% 
  left_join(training_condition, by = c("study_name", "item_num")) %>% 
  mutate(item = )
```

## Testing Part
### Phono_testing
```{r}
study_phono_test <- full_cleanup %>% 
  filter(phase == "phono_test") %>% 
  select(posgreen, posyellow, f_choice, j_choice, study_name, mode, participant, 
         date, phase, phono_test_trial_order, 
         phono_test_item_num, phono_old_new, phono_choice_rt, phono_choice, phono_test_choice_key) %>% 
  rename(trial_order = phono_test_trial_order,
    item_num = phono_test_item_num,
    item_type = phono_old_new,
    rt = phono_choice_rt,
    choice_key = phono_test_choice_key,
    choice = phono_choice) %>% 
  mutate(round = "phono_test") %>% 
  mutate(overall_trial_order = trial_order)
```

# Using condition file to determine regular and random
```{r}
# Phono Testing
testing_phono <- read_csv(here("data", "condition_files", "testing_phono.csv"))

study_phono_test <- study_phono_test %>% 
  left_join(testing_phono) %>% 
  select(-c("choice_A", "choice_B", "choice_stimuli")) %>% 
  mutate(choice = case_when(
    choice_key == "f_key"&f_choice == "choice_A"&choice_A_property == "regular"~"regular",
    choice_key == "f_key"&f_choice == "choice_A"&choice_A_property == "random"~"random",
    choice_key == "f_key"&f_choice == "choice_B"&choice_B_property == "regular"~"regular",
    choice_key == "f_key"&f_choice == "choice_B"&choice_B_property == "random"~"random",
    choice_key == "j_key"&j_choice == "choice_A"&choice_A_property == "regular"~"regular",
    choice_key == "j_key"&j_choice == "choice_A"&choice_A_property == "random"~"random",
    choice_key == "j_key"&j_choice == "choice_B"&choice_B_property == "regular"~"regular",
    choice_key == "j_key"&j_choice == "choice_B"&choice_B_property == "random"~"random",
  )) %>% 
  select(-c("choice_A_property", "choice_B_property"))

study_full_1 <- rbind(study_phono_test, study_training) %>% 
  arrange(match(phase, c("training", "phono_test", "alt_test")))

# Alt_testing
study_alt_test <- full_cleanup %>% 
  filter(phase == "alt_test") %>% 
  select(posgreen, posyellow, f_choice, j_choice, study_name, mode, participant, 
         date, phase, alt_test_trial_order, 
         alt_test_item_num, alt_old_new, alt_choice_property, alt_choice_rt,
         alt_test_choice_key, alt_choice) %>% 
  rename(trial_order = alt_test_trial_order,
    item_num = alt_test_item_num,
    item_type = alt_old_new,
    choice = alt_choice,
    choice_key = alt_test_choice_key,
    rt = alt_choice_rt) %>% 
  mutate(round = "alt_test") %>% 
  mutate(overall_trial_order = trial_order)

testing_alt <- read.csv(here("data", "condition_files", "testing_alt.csv"))

study_alt_test <- study_alt_test %>% 
  left_join(testing_alt) %>% 
  select(-c("choice_A", "choice_B", "choice_stimuli")) %>% 
  mutate(choice = case_when(
    choice_key == "f_key"&f_choice == "choice_A"&choice_A_property == "regular"~"regular",
    choice_key == "f_key"&f_choice == "choice_A"&choice_A_property == "random"~"random",
    choice_key == "f_key"&f_choice == "choice_B"&choice_B_property == "regular"~"regular",
    choice_key == "f_key"&f_choice == "choice_B"&choice_B_property == "random"~"random",
    choice_key == "j_key"&j_choice == "choice_A"&choice_A_property == "regular"~"regular",
    choice_key == "j_key"&j_choice == "choice_A"&choice_A_property == "random"~"random",
    choice_key == "j_key"&j_choice == "choice_B"&choice_B_property == "regular"~"regular",
    choice_key == "j_key"&j_choice == "choice_B"&choice_B_property == "random"~"random",
  )) %>% 
  select(-c("choice_A_property", "choice_B_property", "alt_choice_property"))
```

# Combine everything
```{r}
study_full_final <- 
  rbind(study_full_1, study_alt_test) %>% 
  relocate(c("item_type", "rt"), .after = overall_trial_order)
```

# Create dummy participant identifiers for a better view of the facets
```{r}
study_full_final <- study_full_final %>% 
  arrange(participant) %>% 
  mutate(participant_id = group_indices(., participant))
```

# Final Output
```{r}
write.csv(study_full_final, here("data", "cleaned", paste0("full_process_albert_", Sys.Date(), ".csv")))
```
