---
title: "regression_0616"
author: "Albert"
date: '2022-06-16'
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_folding: hide
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(performance)
library(here)
library(lme4)
library(lmerTest)
library(tidyverse)
library(broom)
library(broom.mixed)
```
Adapted from Thomas' regression_0610.Rmd
```{r}
study <- read.csv(here("data", "new_cleaned_0610", "non_categorical_20220616_albert.csv"))
```

## Pre-modelling preprations
### Mutate regularity
#### Regularity: where, among the yellow (random) choice, does regular component exist
```{r}
study <- study %>% 
  mutate(regularity =  case_when(
    study_name == "study_1" | study_name == "study_3"~"phonotactics",
    study_name == "study_2" | study_name == "study_4"~"alternation",
  ))
```
# Modelling Training
## Preprations
### 1. as.factor()
```{r}
training_modelled <- study %>% 
  mutate(participant =  factor(participant, exclude = c("", NA)),
         study_name =   factor(study_name, exclude = c("", NA)),
         mode =         factor(mode, exclude = c("", NA)),
         phase =        factor(phase, exclude = c("", NA)),
         item_num =     factor(item_num, exclude = c("", NA)),
         training_choice = factor(training_choice, exclude = c("", NA)),
         phono_choice = factor(phono_choice, exclude = c("", NA)),
         alt_choice =   factor(alt_choice, exclude = c("", NA)),
         round =        factor(round, exclude = c("", NA)),
         regularity = factor(regularity, exclude = c("", NA))) %>% 
  filter(phase == "training")
```

### 2. Change reference level to irregular choices, to have an easier interpretation
```{r}
training_modelled$training_choice <- 
  relevel(training_modelled$training_choice, ref = "yellow")
```

### 3. Pre-modelling chekcing
```{r}
study %>% skimr::skim()
```

## Model 1: No interaction
```{r}
no_interaction <-
  glmer(training_choice ~ round + regularity + mode + (1 | participant), 
        data = training_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(no_interaction)
check_collinearity(no_interaction)
```

## Model 2: round*regularity
```{r}
round_regularity_interaction <-
  glmer(training_choice ~ round * regularity + mode + (1 | participant), 
        data = training_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))

summary(round_regularity_interaction)
check_collinearity(round_regularity_interaction)
```

## Model 3: regularity*mode
```{r}
regularity_mode_interaction <-
  glmer(training_choice ~ round + regularity * mode + (1 | participant), 
        data = training_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))

summary(regularity_mode_interaction)
check_collinearity(regularity_mode_interaction)
```

## Model 4: mode*round
```{r}
mode_round_interaction <-
  glmer(training_choice ~ regularity + mode * round + (1 | participant), 
        data = training_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))

summary(mode_round_interaction)
check_collinearity(mode_round_interaction)
```

## Model 5: full interaction
```{r}
full_interaction <-
  glmer(training_choice ~ round * regularity * mode + (1 | participant), 
        data = training_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))

summary(full_interaction)
check_collinearity(full_interaction)
```

## Compare different models
```{r}
anova(full_interaction, no_interaction)

anova(full_interaction, round_regularity_interaction)

anova(full_interaction, regularity_mode_interaction)

anova(full_interaction, mode_round_interaction)
```

## Full interaction
```{r}
summary(full_interaction)
summary(mode_round_interaction)
```

# Modelling Testing Phases
## Preparation of modelling testing phases
Several things to be done here,

### 1. as.factor()
```{r}
testing_modelled <- study %>% 
  mutate(participant =  factor(participant, exclude = c("", NA)),
         study_name =   factor(study_name, exclude = c("", NA)),
         mode =         factor(mode, exclude = c("", NA)),
         phase =        factor(phase, exclude = c("", NA)),
         item_num =     factor(item_num, exclude = c("", NA)),
         training_choice = factor(training_choice, exclude = c("", NA)),
         phono_choice = factor(phono_choice, exclude = c("", NA)),
         alt_choice =   factor(alt_choice, exclude = c("", NA)),
         round =        factor(round, exclude = c("", NA)),
         regularity = factor(regularity, exclude = c("", NA))) %>% 
  filter(phase == "phono_test" | phase == "alt_test") 
```

### 2. change reference level
```{r}
testing_modelled$phono_choice <- relevel(testing_modelled$phono_choice, ref = "vd")
testing_modelled$alt_choice <- relevel(testing_modelled$alt_choice, ref = "vd")
```

### 3. add another factor of regular% to link training and testing phases
```{r}
n_regular <- study %>% 
  group_by(participant, phase, training_choice) %>% 
  mutate(n = n()) %>% 
  filter(phase == "training") %>% 
  group_by(participant, phase) %>% 
  mutate(n_all = n()) %>% 
  select(participant, training_choice, phase, n, n_all) %>% 
  distinct() %>% 
  filter(training_choice == "green") %>% 
  mutate(regular_percent = n/(n_all)) %>% 
  ungroup() %>% 
  select(participant, regular_percent)

n_regular$regular_percent <- formatC(n_regular$regular_percent, digits = 9, format = "f")
length(unique(n_regular$participant))

testing_modelled <- testing_modelled %>% 
  left_join(n_regular)
testing_modelled$regular_percent <- as.numeric(testing_modelled$regular_percent)
```

# Modelling phono testing
```{r}
phono_modelled <- testing_modelled %>% 
  filter(phase == "phono_test")
```
## Model Group 1: No correlation with choices in training phase
### Model 1: No interaction
```{r}
no_interaction_phono <- 
  glmer(phono_choice ~ regularity + mode+ item_type + (1 | participant) + (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(no_interaction_phono)
check_collinearity(no_interaction_phono)
```

### Model 2: regularity*mode
```{r}
regularity_mode_phono <- 
  glmer(phono_choice ~ regularity*mode+ item_type + (1 | participant)+ (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(regularity_mode_phono)
check_collinearity(regularity_mode_phono)
```

### Model 3: regularity*item_type
```{r}
regularity_type_phono <- 
  glmer(phono_choice ~ mode+ regularity * item_type + (1 | participant)+ (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(regularity_type_phono)
check_collinearity(regularity_type_phono)
```
### Model 4: item_type*mode
```{r}
mode_type_phono <- 
  glmer(phono_choice ~ regularity + mode * item_type + (1 | participant)+ (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(mode_type_phono)
check_collinearity(mode_type_phono)
```

### Model 5: full interaction
```{r}
full_interaction_phono <- 
  glmer(phono_choice ~ regularity * mode * item_type + (1 | participant)+ (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(full_interaction_phono)
check_collinearity(full_interaction_phono)
```

### Compare different models
```{r}
anova(full_interaction_phono, mode_type_phono)
anova(full_interaction_phono, regularity_type_phono)
anova(full_interaction_phono, regularity_mode_phono)
anova(full_interaction_phono, no_interaction_phono)
```

## Model Group 2: with correlation with training phase
### Model 1: No interaction
```{r}
no_interaction_phono_cortraining <- 
  glmer(phono_choice ~ regularity + mode+ item_type + regular_percent 
        + (1 | participant)+ (1 + item_num | participant),
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(no_interaction_phono_cortraining)
check_collinearity(no_interaction_phono_cortraining)
```

### Model 2: regularity*mode
```{r}
regularity_mode_phono_cortraining <- 
  glmer(phono_choice ~ regularity*mode+ item_type +regular_percent+
          (1 | participant)+ (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(regularity_mode_phono_cortraining)
check_collinearity(regularity_mode_phono_cortraining)
```

### Model 3: regularity*item_type
```{r}
regularity_type_phono_cortraining <- 
  glmer(phono_choice ~ mode+ regularity * item_type + regular_percent+
          (1 | participant)+ (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(regularity_type_phono_cortraining)
check_collinearity(regularity_type_phono_cortraining)
```

### Model 4: item_type*mode
```{r}
mode_type_phono_cortraining <- 
  glmer(phono_choice ~ regularity + mode * item_type + regular_percent+
          (1 | participant)+ (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(mode_type_phono_cortraining)
check_collinearity(mode_type_phono_cortraining)
```

### Model 5: full interaction
```{r}
full_interaction_phono_cortraining <- 
  glmer(phono_choice ~ regularity * mode * item_type + regular_percent+
          (1 | participant)+ (1 + item_num | participant), 
        data = phono_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(full_interaction_phono_cortraining)
check_collinearity(full_interaction_phono_cortraining)
```

### Compare different models
```{r}
anova(full_interaction_phono_cortraining, mode_type_phono_cortraining)
anova(full_interaction_phono_cortraining, regularity_type_phono_cortraining)
anova(full_interaction_phono_cortraining, regularity_mode_phono_cortraining)
anova(full_interaction_phono_cortraining, no_interaction_phono_cortraining)
```

# Modelling alt testing
```{r}
alt_modelled <- testing_modelled %>% 
  filter(phase == "alt_test")
```

## Model Group 1: No correlation with choices in training phase
### Model 1: No interaction
```{r}
no_interaction_alt <- 
  glmer(alt_choice ~ regularity + mode+ item_type + (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(no_interaction_alt)
check_collinearity(no_interaction_alt)
```

### Model 2: regularity*mode
```{r}
regularity_mode_alt <- 
  glmer(alt_choice ~ regularity*mode+ item_type + (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(regularity_mode_alt)
check_collinearity(regularity_mode_alt)
```

### Model 3: regularity*item_type
```{r}
regularity_type_alt <- 
  glmer(alt_choice ~ mode+ regularity * item_type + (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(regularity_type_alt)
check_collinearity(regularity_type_alt)
```

### Model 4: item_type*mode
```{r}
mode_type_alt <- 
  glmer(alt_choice ~ regularity + mode * item_type + (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(mode_type_alt)
check_collinearity(mode_type_alt)
```

### Model 5: full interaction
```{r}
full_interaction_alt <- 
  glmer(alt_choice ~ regularity * mode * item_type + (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(full_interaction_alt)
check_collinearity(full_interaction_alt)
```

### Compare different models
```{r}
anova(full_interaction_alt, mode_type_alt)
anova(full_interaction_alt, regularity_type_alt)
anova(full_interaction_alt, regularity_mode_alt)
anova(full_interaction_alt, no_interaction_alt)
```

## Model Group 2: with correlation with training phase
### Model 1: No interaction
```{r}
no_interaction_alt_cortraining <- 
  glmer(alt_choice ~ regularity + mode+ item_type + regular_percent 
        + (1 | participant)+ (1 + item_num | participant),
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(no_interaction_alt_cortraining)
check_collinearity(no_interaction_alt_cortraining)
```

### Model 2: regularity*mode
```{r}
regularity_mode_alt_cortraining <- 
  glmer(alt_choice ~ regularity*mode+ item_type +regular_percent+
          (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(regularity_mode_alt_cortraining)
check_collinearity(regularity_mode_alt_cortraining)
```

### Model 3: regularity*item_type
```{r}
regularity_type_alt_cortraining <- 
  glmer(alt_choice ~ mode+ regularity * item_type + regular_percent+
          (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(regularity_type_alt_cortraining)
check_collinearity(regularity_type_alt_cortraining)
```

### Model 4: item_type*mode
```{r}
mode_type_alt_cortraining <- 
  glmer(alt_choice ~ regularity + mode * item_type + regular_percent+
          (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(mode_type_alt_cortraining)
check_collinearity(mode_type_alt_cortraining)
```

### Model 5: full interaction
```{r}
full_interaction_alt_cortraining <- 
  glmer(alt_choice ~ regularity * mode * item_type + regular_percent+
          (1 | participant)+ (1 + item_num | participant), 
        data = alt_modelled,
        family = binomial,
        control=glmerControl(optimizer="bobyqa",
                             optCtrl=list(maxfun=2e5)))
summary(full_interaction_alt_cortraining)
check_collinearity(full_interaction_alt_cortraining)
```

### Compare different models
```{r}
anova(full_interaction_alt_cortraining, mode_type_alt_cortraining)
anova(full_interaction_alt_cortraining, regularity_type_alt_cortraining)
anova(full_interaction_alt_cortraining, regularity_mode_alt_cortraining)
anova(full_interaction_alt_cortraining, no_interaction_alt_cortraining)
```

